\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tikz}

% Define colors
\definecolor{myblue}{RGB}{41, 98, 255}
\definecolor{mygray}{RGB}{128, 128, 128}

% Set up hyperref
\hypersetup{
  colorlinks=true,
  linkcolor=myblue,
  urlcolor=myblue
}

% Define section heading format
\newcommand{\sectionheading}[1]{\vspace{8pt}\noindent\textbf{\textcolor{myblue}{\large #1}}}

% Define itemize format
\setlist[itemize]{label=$\cdot$, leftmargin=16pt, itemsep=4pt}

% Define entry command for work and education experiences
\newcommand{\entry}[4]{
  \noindent \textbf{#1} \hfill #2 \\
  \textit{#3} \hfill \textit{#4} \\
  \vspace{4pt}
}

% Define command for skill level bars
\newcommand{\skills}[2]{%
  \begin{tikzpicture}
    \fill[myblue, myblue] (0,0) rectangle (#2,0.4);
    \fill[white, myblue] (#2,0) rectangle (5,0.4);
    \draw (0,0) rectangle (5,0.4);
    \node[anchor=west] at (5.2,0.2) {#1};
  \end{tikzpicture}%
}

\begin{document}

\begin{center}
  \textbf{\LARGE \textcolor{myblue}{Your Name}} \\
  \vspace{4pt}
  \textcolor{mygray}{\textit{Your Profession}} \\
  \vspace{8pt}
  \url{www.yourwebsite.com} $\vert$ your.email@example.com $\vert$ (123) 456-7890
\end{center}

\vspace{8pt}

\sectionheading{\textcolor{myblue}{Summary}}
Your summary goes here. Briefly highlight your skills, experience, and achievements.

\vspace{8pt}

\sectionheading{\textcolor{myblue}{Experience}}
\newline
\entry{Company A}{City, Country}{Position}{Dates}
Description of your responsibilities and accomplishments at Company A.

\entry{Company B}{City, Country}{Position}{Dates}
Description of your responsibilities and accomplishments at Company B.

\vspace{8pt}

\sectionheading{\textcolor{myblue}{Education}}
\newline
\entry{University A}{City, Country}{Degree}{Dates}
Description of your studies and any notable achievements at University A.

\entry{University B}{City, Country}{Degree}{Dates}
Description of your studies and any notable achievements at University B.

\vspace{8pt}

\sectionheading{\textcolor{myblue}{Skills}}
\begin{itemize}
  \item Skill 1 \skills{Intermediate}{3.5}
  \item Skill 2 \skills{Advanced}{4.5}
  \item Skill 3 \skills{Beginner}{2.0}
\end{itemize}

\vspace{8pt}

\sectionheading{\textcolor{myblue}{Projects}}
\newline
\entry{Project A}{Description}{Technologies}{Dates}
Brief overview of your project A and the technologies used.

\entry{Project B}{Description}{Technologies}{Dates}
Brief overview of your project B and the technologies used.

\vspace{8pt}

\sectionheading{\textcolor{myblue}{Certifications}}
\newline
\entry{Certification A}{Certifying Organization}{Dates}{Credential ID}
Description of your certification A and any relevant details.

\entry{Certification B}{Certifying Organization}{Dates}{Credential ID}
Description of your certification B and any relevant details.

\vspace{8pt}

\sectionheading{\textcolor{myblue}{Publications}}
\newline
\entry{Publication A}{Journal/Conference}{Authors}{Year}
Summary of your publication A and any key findings.

\entry{Publication B}{Journal/Conference}{Authors}{Year}
Summary of your publication B and any key findings.

\vspace{8pt}

\sectionheading{\textcolor{myblue}{Interests}}
\begin{itemize}
  \item Interest 1
  \item Interest 2
  \item Interest 3
\end{itemize}

\end{document}
